\LARGE \bf On the Commissioning of the 12 GeV HMS Drift Chambers, Electronics/Computer Dead Time Monitoring and Overview of the D(e,e'p)n Experimental Run Plan

### 2017-10-25 NRF_Final_Report/report.tex
finished section on drft chambers

  \caption{Comparison of the current drawn in the HMS and SHMS chambers for different gas mixtures. The subplot shows a zoomed version of the HMS DC II plot on a small scale.}

@@

significant current drawn allows for a better determination of the \textit{Plateau Region} of the chambers, which is a region in which the chamber efficinecies have little sensitivity
to relatively large High Voltage variations of $\sim$40 V. \\

@@

certain time window. This requirement ensures a correlation between the top and bottom PMT signals, making it highly probable that the signal was produced by a cosmic ray. 

@@

When cosmic data was taken, to ensure that all (or at leas most) of the sense wires in each plane were present (and had not been damaged by transporting the chamber), the wiremap distribution was

@@

by setting the threshold fixed at 4.5 V. The optimal HV setting was determined to be 1940 V. A threshold scan was then performed at 1940 V to determine the optimal threshold. The results are shown in Figures

@@

  \label{fig:hdc2_wire}

@@

  \label{fig:hdc2_wire}

@@

>>>>

  \caption{Comparison of the current drawn in the HMS and SHMS chambers for different gas mixtures. The subplot shows a zoomed version of the Argon/Ethane gas mixture used in HMS DC II plot on a nanoampere scale.}

@@

significant current drawn allows for a better determination of the \textit{Plateau Region} of the chambers, which is a region in which the chamber efficiencies have little sensitivity
to relatively large High Voltage variations. \\

@@

certain time window. This requirement ensures a correlation between the top and bottom PMT signals, making it highly probable that the signal was produced by a cosmic ray. The correlated signal between the top and
bottom PMTs is defined as the \textit{trigger}. The efficiency of the \textit{i$^{th}$} plane, $\epsilon_{i}$, can then be defined as follows,
\begin{equation}
\epsilon_{i} = \frac{\# \text{ triggers that \textit{did} hit the \textit{i$^{th}$} plane } }{\# \text{ triggers that \textit{should} have hit the \textit{i$^{th}$} plane} } 
\end{equation}
given that the other five planes received at least one hit from the cosmic. \\
\indent To make a reliable efficiency measurement, it has to be ensured from the geometry of the cosmic set-up, that any cosmic passing though the top and bottom scintillators also traverses every plane in the chamber
to make the efficiency measurements unbiased to the scintllators orientation. 

@@

When cosmic data was taken, to ensure that all (or at least most) of the sense wires in each plane were present (and had not been damaged by transporting the chamber), the wiremap distribution was

@@

by setting the threshold fixed at 4.5 V to determine the optimal HV setting. A threshold scan was then performed at 1940 V to determine the optimal threshold. The results are shown in Figures \ref{fig:hdc2_hvscan}
and \ref{fig:hdc2_thrsscan}. The high voltage scan in Figure \ref{fig:hdc2_hvscan} shows the plateau region starting at 1900 V. The chamber operational high voltage was chosen to be 1940 V since the efficiencies seem
to be stable and better than 99$\%$ over a $\sim\pm$40 Volt range about this central setting.

@@

  \caption{High Voltage scan of DC II over a broad range at a Threshold of 4.5 Volts.}
  \label{fig:hdc2_hvscan}
\end{figure} 

@@

  \caption{Threshold scan over a broad range at a HV setting of 1940 V.}
  \label{fig:hdc2_thrsscan}

@@

From the threshold scan results in Figure \ref{fig:hdc2_thrsscan}, there is a 3$\%$ decrease in the plane efficiencies over a
6 Volt range. The operational threshold voltage was determined to be 4.5 Volts, where the efficiencies are better than 99$\%$, over a $\sim$ 1 Volt range.
The high voltage and threshold settings determined from the scans were chosen based on the high efficiency region and its small sensitivity over a voltage range.
